---
title       : Developing Data Products - Slidify Project
subtitle    : USA arrests in 1973 by States
author      : Sebastián Fuenzalida Garcés
job         : September 27, 2015
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
---

## What does the application do?

The application allows you to do an Exploratory Data Analysis to the "USArrests" dataset focused in:  

1. Maps: Graphic Map with the number of arrests in 1973 for Murder, Assault and Rape by State and the urban population in that year  
2. Compare: Barplots that compare differente zones of USA like North vs South or West vs Central, to check the states or zones with more arrests  
3. DataSet: You can check the complete dataset  

You can try the application [here](https://sfuenza.shinyapps.io/Developing-Data-Product---Project).

--- .class #id 

## The Data Set

The original USArrests dataset consists in 5 columns and 50 rows one for each state:
```{r dataset, echo=FALSE}
print(head(USArrests))
```
For the analysis a couple of changes were done:
* All the names of the states were change to lowercase to use a map of states data set that allows us to draw USA and Alaska was erase because it wasn't in the graphic map
* Two new columns were included:
      * North_South: Indicates if the State is in the North or South of USA
      * West_Central_East: Indicates if the State is in the West, Central or East of USA

--- .class #id

## How it works?

When you enter to the app you have 3 sections:

* Upper Navigation: Allows you to switch between the analyze section to the information to know a little bit more of the app
* Left Panel: Here you can select the States that are going to be included in the graphics and the dataset
* Main Panel: Here is where the graphics and the dataset are shown, you can switch between:
      * Maps: States Map comparison
      * Compare: Comparison between zones and states with barplots
      * Data Set: The complete data set as a table to check it


--- .class #id

## Example

Here you can see an example of the graphic map of USA:

```{r load_map, echo=FALSE, message=FALSE, fig.align='center'}
library(maps)
library(ggplot2)
arrests<-read.csv("libraries/USArrests.csv",header=TRUE,sep=";")
map_of_states<-map_data("state")
p <- ggplot(arrests, aes(map_id = State))
p <- p + geom_map(aes_string(fill = "Murder"), map = map_of_states, colour='gray')
p <- p + expand_limits(x = map_of_states$long, y = map_of_states$lat)
p <- p + coord_map() + theme_bw()
p <- p + labs(x = "Longitude", y = "Latitude",title="N° of arrests for Murder in USA in 1973")
p  + scale_fill_gradient(low = "yellow", high = "red", na.value = "black")


```



